Machines are Among Us

### 2020-12-03 paper/main.tex
almost there. mainly just abstract left

\subsection{Modeling Interpretation and Communication}
In order to process the input events, our agent model has an LSTM, which
generates $c_N$ and $h_N$, which are used as the initial inputs
$h_0$ and $c_0$ to the next phase:
communication. Communcation is also modeled with an LSTM. During each ``round''
of communication, every agent contributes a message vector of size $M$ via
a small MLP using $h_t$ as input. These messages are collected into a matrix
of size $M \times P$, which is fed as input into each agent's LSTM so that
their memory can be updated before the next round of communication -- there
are $R$ rounds in total. We chose
to model communication this way because it is a simple and symmetric way for the agents
to pass information between each other in multiple rounds.

@@

Another important challenge to recognize is the extreme "black box" architecture
of the model. With our current model iteration, we have no current approach to visualizing
exactly what the model is doing, especially with communication. Therefore there are
assumptions and estimations when creating conclusions about the model.
\subsection{Situation Hyperparameters}
To list the variable hyperparameters and input and outputs sizes for the player model,
overall, we have batch size, number of epochs, epoch length, the global LSTM hidden layer size, 
and the amount of players and imposters. For the perception phase, there is the
chance a player will view another player, the chance a sabotage occurs, and the number of $N$ events.  
The communication stage has variables the message size $M$ and the number of communication rounds
$R$.
\begin{figure*}
   \begin{center}
      \includegraphics[width=0.8 \textwidth]{img/grid_search.png}
   \end{center}
      \caption{A grid search heat map over the size parameters M (message vector) 
      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs.
      }
   \label{fig:model}
\end{figure*}
\section{Results}
% talk about our goal for a qualitatively "good" communication
% session.
Due to the unprecedented architecture, we decided our overall goals
were to find the balance between imposter and crew
score, locate trends within the variable changes, and attempt to 
understand how the models communicate, to a degree. We conducted many
training sessions over multiple different combinations of variables.

A typical training session started with the first two alternating epochs,
which were considered as the "initialization" of the two models. Training the imposters
first gave them time to learn to note vote for each other. Then, the crew
had learned the same thing on the next epoch. After this initial training,
then the models started to significantly train against each other.

@@

\subsection{Oscillating Scores}
The hopeful goal was to find the set of variables that lead to not only a convergence,
but an almost "tug-of-war" battle when one model trains against the other and vice versa.
This is graphically shown via an oscillating crew score around the 
eventual convergence crew score. This would mean that the two models
are successfunlly balanced and able to improve their strategy with training time against
the opposition.

\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
Unfortunately, we could not fully interpret the communication vectors due to the
disconnect between representation of information. However, we found an 
interesting result when the players were given no identifying information (e.g. 
there were no sabotages whatsoever in the percpetion stage), the crew could still
win the situation. At first glance, this seems almost impossible because the crew would
be unable to identify the imposters via the necessary events. Further thought lead us
to make an estimated conclusion that the crew model was actual creating a hidden tag or key
to identify themselves within the commmunication stage, therefore identifying the imposters 
immediately. The imposters would then have to train to figure out this key or
become helpless. This situation resembles almost a cryptographic adversarial problem,
unlocking more future directions this work could potentially travel.
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
\appendix
\section{Reproducibility}
Reproducibility might yield different results due to the random creation of data and
weight setting.

The parameters used for Figure 2, the grid search, are:

\begin{tabular}{ |c|c| } 
\hline 
"B" & 64 \\
\hline
"N" & 16 \\
\hline
"H"& 256 \\
\hline
"M"& 12 \\
\hline
"ROUNDS"& 0 \\
\hline
"P"& 10 \\
\hline
"I"& 2 \\
\hline
"EPOCHS"& 6 \\
\hline
"EPOCH LENGTH"& 1024 \\
\hline
"VIEW CHANCE"& 0.5 \\
\hline
"SABOTAGE CHANCE"& 0.5 \\
\hline
"TRAIN CREW FIRST"& false \\
\hline
"TRAIN SINGLE CREWMATE"& true \\
\hline
"CONST CREW COPY FREQ"& 32 \\
\hline
"TRAIN SINGLE IMPOSTER"& true \\
\hline
"CONST IMPOSTER COPY FREQ"& 32 \\
\hline
"PRINT FREQ"& 64 \\
\hline
"SAVE EPOCH FREQ"& 2 \\
\hline
\end{tabular}
\section{Framework}
The framework we used for our project
was PyTorch, and build the model based off of their implementation
of an LSTM and MLP layers. 
\end{document}

>>>>

\subsection{Modeling Interpretation and Communication}
In order to process the input events, our agent model has an LSTM, which
generates $c_N$ and $h_N$, which are used as the initial inputs
$h_0$ and $c_0$ to the next phase:
communication. Communcation is also modeled with an LSTM. During each ``round''
of communication, every agent contributes a message vector of size $M$ via
a small MLP using $h_t$ as input. These messages are collected into a matrix
of size $M \times P$, which is fed as input into each agent's LSTM so that
their memory can be updated before the next round of communication -- there
are $R$ rounds in total. We chose
to model communication this way because it is a simple and symmetric way for the agents
to pass information between each other in multiple rounds.
Figure \ref{fig:model} shows a simplified diagram of the complete
architecture.

@@

Another important challenge to recognize is the extreme "black box" architecture
of the model. With our current model iteration, we have no current approach to visualizing
exactly what the model is doing, especially with communication. Therefore there are
assumptions and estimations when creating conclusions about the model.
\subsection{Situation Hyperparameters}
To list the variable hyperparameters and input and outputs sizes for the player model,
overall, we have batch size, number of epochs, epoch length, the global LSTM hidden layer size, 
and the amount of players and imposters. For the perception phase, there is the
chance a player will view another player, the chance a sabotage occurs, and the number of $N$ events.  
The communication stage has variables the message size $M$ and the number of communication rounds
$R$.
\begin{figure*}
   \begin{center}
      \includegraphics[width=0.8 \textwidth]{img/grid_search.png}
   \end{center}
      \caption{A grid search heat map over the size parameters M (message vector) 
      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs. Figure \ref{tab:params} contains the other parameters used.
      }
   \label{fig:grid}
\end{figure*}
\section{Results}
Due to the unprecedented architecture, we decided our overall goals
were to find the balance between imposter and crew
score, locate trends within the variable changes, and attempt to 
understand how the models communicate, to a degree. We conducted many
training sessions over multiple different combinations of variables.

A typical training session started with the first two alternating epochs,
which were considered as the "initialization" of the two models. Training the imposters
first gave them time to learn to not vote for each other. Then, the crew
had learned the same thing on the next epoch. After this initial training,
then the models started to significantly train against each other.

@@

\subsection{Oscillating Scores}
The hopeful goal was to find the set of variables that lead to not only a convergence,
but an almost "tug-of-war" battle when one model trains against the other and vice versa.
This is graphically shown via an oscillating crew score around the 
eventual convergence crew score. This would mean that the two models
are successfunlly balanced and able to improve their strategy with training time against
the opposition. Figure \ref{fig:osc} shows an example of a single run which converges
to a crew score of around 0.6.
\begin{figure}[h]
   \begin{center}
      \includegraphics[width=0.47827\textwidth]{img/m16_r10.png}
   \end{center}

   \label{fig:osc}
   \caption{Crew score over time for a particular training run. The crew model is
   being trained in odd epochs, and imposters in even epochs.}
\end{figure}

\subsection{Interpreting Communcation Vectors}
Unfortunately, we were not able to interpret the communication vectors due to the
disconnect between representation of information. However, we found an 
interesting result when the players were given no identifying information (e.g. 
there were no sabotages whatsoever in the percpetion stage), the crew could still
win the situation. At first glance, this seems almost impossible because the crew would
be unable to identify the imposters via the necessary events. Further thought lead us
to make an estimated conclusion that the crew model was actual creating a hidden tag or key
to identify themselves within the commmunication stage, therefore identifying the imposters 
immediately. The imposters would then have to train to figure out this key or
become helpless. This situation resembles almost a cryptographic adversarial problem,
unlocking more future directions this work could potentially travel.
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
\appendix
\section{Reproducibility}
The code that we used to train, test, and plot graphics for the models
is in a public GitHub repository at \url{https://github.com/quinquice/mendax}.
Note that due to random data generation and unpredictable training, it may be
difficult to reproduce the exact graphs we have in this paper, but similar results
should be attainable.

\begin{figure}
   \centering
\begin{tabular}{ |c|c| } 
\hline 
"B" & 64 \\
\hline
"N" & 16 \\
\hline
"H"& 256 \\
\hline
"P"& 10 \\
\hline
"I"& 2 \\
\hline
"EPOCHS"& 6 \\
\hline
"EPOCH LENGTH"& 1024 \\
\hline
"VIEW CHANCE"& 0.5 \\
\hline
"SABOTAGE CHANCE"& 0.5 \\
\hline
"TRAIN CREW FIRST"& false \\
\hline
"TRAIN SINGLE CREWMATE"& true \\
\hline
"CONST CREW COPY FREQ"& 32 \\
\hline
"TRAIN SINGLE IMPOSTER"& true \\
\hline
"CONST IMPOSTER COPY FREQ"& 32 \\
\hline
\end{tabular}
\caption{The parameters used for Figure \ref{fig:grid}, the grid search}
\label{tab:params}
\end{figure}

\section{Framework}
The framework we used for our project
was PyTorch, and build the model based off of their implementation
of an LSTM and MLP layers. Models were trained on a variety of different
computers, sometimes with CPU and sometimes with GPU.

\end{document}
